00_datawrangling.Rmd

### 2019-12-20 analysis/00_datawrangling.Rmd
specifitity, isoforms, and gon vsd

# check for genes that have multple transcripts expressed
isoforms <- kallistodata %>%
  group_by(Name) %>%
  summarize(n = n()) %>%
  arrange(desc(n), Name) %>%
  filter(n > 1)
head(isoforms)

>>>>

# check for genes that have multple transcripts expressed
isoforms <- kallistodata %>%
  group_by(Name) %>%
  summarize(n = n()) %>%
  filter(n > 1) %>%
  group_by(n) %>% 
  summarize(genes = str_c(Name, collapse = ", ")) %>%
  arrange(desc(n)) %>%
  rename("n(isoforms)" = "n") %>% 
  mutate("n(counts)" = str_count(genes, ",") + 1)
head(isoforms)
